---
title: "Twitter API Authorization"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{auth}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(tweetbotornot2)
```

This vignette provides background and addresses commonissues related to 
obtaining access (authorization) to Twitter's APIs. It also introduces two
authorization methods–the default (user) authorization method and the
application-only (bearer) authorization method–and explains some key differences
between the two.

## Authentication

Use of {tweetbotornot} typically<sup>1</sup> requires, at a minimum, (a) internet 
connection and (b) an active Twitter account. The latter is needed because 
Twitter requires authentication prior to use of their REST API. As a result, to
use key functions of {tweetbotornot}, users must either approve the embedded 
{rtweet} *rstats2twitter* application (this allows {rtweet} to communicate from 
R to Twitter's APIs) or provide their own application and account credentials. 
If a user is already signed into Twitter in their default web browser, this can
be done with a single click. Otherwise, users must sign-in to Twitter and 
*then* click.

## Saving/using Twitter API token

If you're working in an interactive R session on a local machine (in the RStudio 
application, for example), this process should be relatively straight forward.<sup>1</sup>
However, if you're working on a remote server or in the cloud (in RStudio Server,
for example), then it's a bit trickier. The easiest solution is to start a local, 
interactive session of R and then do the following:

1. **On a machine with a local version of R**, send API request via {rtweet}
   ```{r, eval=FALSE}
   rstats <- rtweet::search_tweets("rstats")
   ```
1. The above code actually creates (as a side effect) a Twitter token for you. So, on the same machine, save the token as an `.rds` file
   ```{r, eval=FALSE}
   saveRDS(rtweet::get_token(), "rtweet_token.rds")
   ```
1. Upload the saved token file to your **cloud/server**
1. Once the token is uploaded to the cloud, you can read the token file and 
specify the resulting object in each {tweetbotornot} call, e.g.,
   ```{r, eval=FALSE}
   token <- readRDS("rtweet_token.rds")
   predict_bot("jack", token = token)
   ```
   or set the path to the saved token as an R environment variable. The latter 
   option (example below) allows you to avoid having to specify the token each time.
   ```{r, eval=FALSE}
   Sys.setenv(TWITTER_PAT = "/path/to/rtweet_token.rds")
   predict_bot("jack")
   ```
   or set the R environment variable for current **and** future sessions (on a
   given machine), you can also try `tfse::set_renv()`.
   ```{r, eval=FALSE}
   tfse::set_renv(TWITTER_PAT = "/path/to/rtweet_token.rds")
   ```

## Authorization methods & rate limits

Assuming users haven't made any recent calls to Twitter's API, the predict functions
described earlier should work for up to 900 users at a time. For some users (e.g., those with a Twitter 
token created using credentials from their own Twitter application or tokens 
created at a time of sufficiently provided permissions by the embedded rtweet app)
it's possible to get estimates for up to 1,500 accounts at a time using Twitter's
application-only (bearer) token. Converting a normal user token into a bearer 
token requires an access level of `"read-write-directmessages"`. The code below 
should print the access level associated with your current token.

```{r, eval=FALSE}
## view access level of current token
print(rtweet:::api_access_level())
```

The drawback to the application-only authorization method is that your requests
will contain no information about the authenticating user. The upside to this
kind of token is access to a different set of rate limits. The different rate 
limits aren't always desirable (compared to the normal user token), but for the
some endpoints–like `users/timelines` (900 vs. 1,500 requests per 15 min.) and
`search/tweets` (18,000 vs. 45,000 requests per 15 min.)–the difference is quite 
significant.

If the output from the above code was `"read-write-directmessages"`, then users
can specify the bearer token via `rtweet::bearer_token()` for the `token` argument
in bot-predicting calls. The code below, for example, checks the bearer token rate
limit before and after executing `predict_bot()`.

```{r, eval=FALSE}
## check bearer token rate limit
rtweet::rate_limit(rtweet::bearer_token(), "get_timeline")

## get bot estimates for two users
predict_bot(c("netflix_bot", "PatrickMahomes"), token = rtweet::bearer_token())

## re-check bearer token rate limit
rtweet::rate_limit(rtweet::bearer_token(), "get_timeline")
```
