---
title: "example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
## load package
library(tweetbotornot2)
```


## Authentication

Use of this package typically<sup>1</sup> requires, at a minimum, (a) internet 
connection and (b) an active Twitter account–i.e., you will need to authorize
rtweet's *rstats2twitter* app to act (communicate from R to Twitter) on behalf 
of your Twitter account. If you're already signed into Twitter on your web 
browser, this can be done with a single click. Otherwise, you will have to sign 
in and *then* click.

If you're working in an interactive R session on a local machine (in the RStudio 
application, for example), this process should be relatively straight forward.
<sup>1</sup> If you're working on a remote server or in the cloud (in RStudio 
Server, for example), then it's a bit trickier. The easiest solution is to start 
a local, interactive session of R and then do the following:

1. **On a machine with a local version of R**, send API request via {rtweet}
   ```{r, eval=FALSE}
   rstats <- rtweet::search_tweets("rstats")
   ```
1. The above code actually creates (as a side effect) a Twitter token for you. So, on the same machine, save the token as an `.rds` file
   ```{r, eval=FALSE}
   saveRDS(rtweet::get_token(), "rtweet_token.rds")
   ```
1. Upload the saved token file to your **cloud/server**

Once the token is uploaded to the cloud, you can either read the token file and 
specify the resulting object in each {tweetbotornot} call, e.g.,
```{r, eval=FALSE}
token <- readRDS("rtweet_token.rds")
predict_bot("jack", token = token)
```

or set the path to the saved token as an R environment variable. The latter 
option (example below) allows you to avoid having to specify the token each time.

```{r, eval=FALSE}
Sys.setenv(TWITTER_PAT = "/path/to/rtweet_token.rds")
predict_bot("jack")
```

To set the R environment variable for current **and** future sessions (on a
given machine), you can also try `tfse::set_renv()`.

```{r, eval=FALSE}
tfse::set_renv(TWITTER_PAT = "/path/to/rtweet_token.rds")
```

## Bot scores

The main use of this package is to get bot-probability estimates of one or more
Twitter accounts. This can be done with the `predict_bot()` function.

```{r, eval=FALSE}
predict_bot(c("netflix_bot", "PatrickMahomes"))
```

### Rate limits

Assuming you haven't made any recent calls to Twitter's API, the above function
should work for up to 900 users at a time. If you are able to convert your Twitter
token into a bearer token with {rtweet} (this is not always possible; it depends
on a number of things; try the code below to see if you can), you should be able
to get estimates for up to 1,500 accounts at a time. You can use the following
code to see if the bearer token will work for you.

```{r, eval=FALSE}
## specify token if R environment variable isn't set
rtweet::search_tweets("rstats", token = rtweet::bearer_token())
```

If the above code returns a data frame of tweets data, then you can specify the
bearer token in `predict_bot()` the same way. The code below checks your bearer
token rate limit before and after executing `predict_bot()`.

```{r, eval=FALSE}
rtweet::rate_limit(rtweet::bearer_token(), "get_timeline")
predict_bot(c("netflix_bot", "PatrickMahomes"), token = rtweet::bearer_token())
rtweet::rate_limit(rtweet::bearer_token(), "get_timeline")
```

### Example users

For example purposes, this vignette retrieves user IDs from accounts appearing
on a Twitter list of 2020 Democratic presidential candidates.

```{r, eval=FALSE}
## get accounts from the twitter list: twitter.com/kearneymw/lists/dems-pres-2020
d20 <- rtweet::lists_members(owner_user = "kearneymw", slug = "dems-pres-2020")

## store IDs as 'users' vector
users <- d20$user_id
```

### Making large requests

To get estimates for hundreds or thousands of users, it is wise to use a for-loop 
and wait for the rate limit reset by sleeping between calls. This can be done in a number
of ways, but the functions `chunk_users()` and `chunk_users_data()` are provided
to make this easier. The code below should work for either user or bearer (rtweet)
token. It also prints out rate limit information and percent complete information.

```{r, eval=FALSE}
## convert users vector (user IDs or screen names) a list of 10-user chunks
users <- chunk_users(users, n = 10)

## initialize output vector
output <- vector("list", length(users))

for (i in seq_along(output)) {
  ## check rate limit- if < 10 calls remain, sleep until reset
  print(rl <- rtweet::rate_limit(query = "get_timelines"))
  while (rl[["remaining"]] < 10L) {
    cat("Sleeping for", round(max(as.numeric(rl[["reset"]], "mins"), 0.5), 1), "minutes...")
    Sys.sleep(max(as.numeric(rl[["reset"]], "secs"), 30))
    rl <- rtweet::rate_limit(query = "get_timelines")
  }
  
  ## get bot estimates
  output[[i]] <- predict_bot(users[[i]])
  
  ## print iteration update
  cat(sprintf("%d / %d (%.f%%)\n", i, length(output), i / length(output) * 100))
}

## merge into single data table
output <- do.call("rbind", output)

## sort by bot probability
output[order(-prob_bot), ]
```

If you'd also like to keep the raw (timeline) Twitter data, the above for loop
can be modified to collect the Twitter data prior to generating estimates with
`predict_bot()`. This is demonstrated in the code below.

```{r, eval=FALSE}
## convert users vector (user IDs or screen names) a list of 10-user chunks
users <- chunk_users(users, n = 10)

## initialize output vectors
output <- vector("list", length(users))
usrtml <- vector("list", length(users))

for (i in seq_along(output)) {
  ## check rate limit- if < 10 calls remain, sleep until reset
  print(rl <- rtweet::rate_limit(query = "get_timelines"))
  while (rl[["remaining"]] < 10L) {
    cat("Sleeping for", round(max(as.numeric(rl[["reset"]], "mins"), 0.5), 1), "minutes...")
    Sys.sleep(max(as.numeric(rl[["reset"]], "secs"), 30))
    rl <- rtweet::rate_limit(query = "get_timelines")
  }
  
  ## get user timeline data (set check=FALSE to avoid excessive rate-limit calls)
  usrtml[[i]] <- rtweet::get_timelines(users[[i]], n = 200, check = FALSE)
  
  ## use the timeline data to get bot estimates
  output[[i]] <- predict_bot(users[[i]])
  
  ## print iteration update
  cat(sprintf("%d / %d (%.f%%)\n", i, length(output), i / length(output) * 100))
}

## merge both data lists into single data tables
output <- do.call("rbind", output)
usrtml <- do.call("rbind", usrtml)

## sort by bot probability
output[order(-prob_bot), ]

## preview timeline data
usrtml[1:10, ]
```


<sup>1</sup> Unless you've already collected user timeline data, **[`{tweetbotornot2}`](tweetbotornot2.mikewk.com)** 
relies on [`{rtweet}`](https://rtweet.info) to pull data from [Twitter's REST API](https://developer.twitter.com/en/docs).

<sup>2</sup> The first time you make a request [from your computer] to Twitter's API's, a 
browser should pop-up, asking you to authorize the app. After that, the
authorization token is stored and remembered behind the scenes (you will only 
have to reauthorize the app if your Twitter settings or token credentials get 
reset or if you use a different machine).
